New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/schur.tex
taux de croissance
version finale 07/04

\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction. 
Rolwey named these partitions "templates", and we will keep this name in the entire article. Finding suitable templates and applying his 
method to these will allow us to find new lower bounds for Schur methods.

@@

\subsection{Inequaties on \(SE_+\)}

@@

\begin{theorem}
	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$
\end{theorem}

@@

>>>>

\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's [8] construction. 
Rolwey named these partitions "templates", and we will keep this name in the entire article. We find suitable templates and use them
 to find new lower bounds for Schur numbers.

@@

\subsection{Inequalities on \(SE_+\)}

@@

\begin{theorem}
	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$.
\end{theorem}

@@

\begin{corollary}
The growth rate for Schur (and Ramsey) numbers satisfies \(\gamma = \sqrt[5]{380} \geqslant 3.28 \).
\end{corollary}
\textsc{Proof :} It is a mere consequence of the inequality \(380S(n-5) + 148 \leqslant S(n) \). As for Ramsey's 
numbers growth rate, a lower bound can be found using Schur's one, thanks to \(S(n) \leqslant R_n(3)-2 \) 
(see \hyperlink{label1}{\textbf{[1]}}).
